Evaluation of clustering parameters - SCPCS000169

### 2024-08-02 analyses/cell-type-wilms-tumor-06/notebook/01-clustering_SCPCS000169.Rmd
Update 01-clustering_SCPCS000169.Rmd
Because of data download with the download-data.py method. Update paths

In the chunk below, we include some common directories that you might need, finding their locations using the very useful [`rprojroot` package](https://rprojroot.r-lib.org/).

Note for the DataLab, not sure what to do with this, I decided to use paths below.

```{r base paths, eval=FALSE, include=FALSE}
# The base path for the OpenScPCA repository, found by its (hidden) .git directory
repository_base <- rprojroot::find_root(rprojroot::is_git_root)

# The current data directory, found within the repository base directory
data_dir <- file.path(repository_base, "data", "current")

# The path to this module
module_base <- file.path(repository_base, "analyses", "{{openscpca_module}}")
```

@@

In our case, the SCPCP000006 dataset downloaded the 25-06-2024 is locally saved in /mnt_data/Wilms ALSF/SCPCP000006_2024-06-25.
Please mount your local folder of data accordingly or change the path below. Ideally, the mnt_data is set up in the config.yaml file

```{r paths}
# input
# please mount your local folder of data accordingly or change the path below. ideally, the mnt_data is set up in the config.yaml file
path_to_data <- "~/mnt_data/Wilms ALSF/SCPCP000006_2024-06-25"

# get all files in the data directory
filelist <- list.files(path_to_data, full.names = TRUE)

# select the 40 Wilms tumor single nucleus folders only
filelist <- filelist[grepl("/mnt_data/Wilms ALSF/SCPCP000006_2024-06-25/SCPC", filelist)]

# output
## html report for each of the Wilms tumor sample will be saved in 
path_to_report <- "~/notebook/01-clustering"
## some plots from the report will be saved in 
path_to_plot <- "~/plots"
## after final decision on the clustering strategy, processed RDS files will be saved in 
path_to_result <- "~/results"
```

```{r paths2}
## to be modified when rendered
i = 2
filedir <- filelist[i] 
sample <- gsub("/home/rstudio/mnt_data/Wilms ALSF/SCPCP000006_2024-06-25/", "", filedir)

metadata <- read.table("SCPCP000006_metadata.tsv", sep = "\t", header=TRUE)

>>>>

```{r base paths, eval=TRUE, include=TRUE}
# The base path for the OpenScPCA repository, found by its (hidden) .git directory
repository_base <- rprojroot::find_root(rprojroot::is_git_root)

# The current data directory, found within the repository base directory
data_dir <- file.path(repository_base, "data", "2024-07-08", "SCPCP000006")

# The path to this module
module_base <- file.path(repository_base, "analyses", "cell-type-wilms-tumor-06")
```

@@

```{r paths}
# input
# use download-data.py to download the data

# get all files in the data directory
filelist <- list.files(data_dir, full.names = TRUE)

# select the 40 Wilms tumor single nucleus folders only
filelist <- filelist[! grepl(".tsv", filelist)]

# output
## html report for each of the Wilms tumor sample will be saved in 
path_to_report <- file.path(module_base, "01-clustering")
## some plots from the report will be saved in 
path_to_plot <- file.path(module_base, "/plots")
## after final decision on the clustering strategy, processed RDS files will be saved in 
path_to_result <- file.path(module_base, "/results")
```

```{r paths2}
## to be modified when rendered
i = 2
filedir <- filelist[i] 
sample <- gsub(paste0(data_dir, "/"), "", filedir)

metadata <- read.table(file.path(data_dir, "/single_cell_metadata.tsv"), sep = "\t", header=TRUE)
